\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-04-26 main.Rmd
added a couple of sentences to future work

When `polar = TRUE`, a polar transformation is carried out on the data. The computation is similar to the one described in @Wickham2012glyph. The resulting plot is star glyphs embedded in the monthly calendar layout. Star glyphs are time series lines transformed in polar coordinates.

@@

```{r calendar-elec, fig.height = 10.5, fig.cap = "Calendar displays for each household using common scales. We can precisely tell each indidual's vacation days to take off and the overnight use for household 2."}
```

@@

The methodology creates the western calendar layout, because most countries have adopted this format. The main difference between countries is the use of different languages for labeling, which is supported by the software. Layouts beyond the western calendar could be achieved by the same modular arithmetic approach.

The calendar layout will be useful for studying consumer trends and human behavior. It will not be so useful for physical patterns like climate, which are not typically affected by human activity. The layout does not replace traditional displays, but serves to complement to further tease out structure in temporal data. Analysts would still be advised to plot overall summaries and deviations in order to study general trends.

>>>>

When `polar = TRUE`, a polar transformation is carried out on the data. The computation is similar to the one described in @Wickham2012glyph. The resulting plot is star glyphs---time series lines transformed in polar coordinates---embedded in the monthly calendar layout.

@@

```{r calendar-elec, fig.height = 10.5, fig.cap = "Calendar displays for each household using common scales. We can precisely tell each indidual's vacation days taking off and the overnight use for household 2 in mid January."}
```

@@

The calendar layout will be useful for studying consumer trends and human behavior. It will be less useful for physical patterns like climate, which are not typically affected by human activity. The layout does not replace traditional displays, but serves to complement to further tease out structure in temporal data. Analysts would still be advised to plot overall summaries and deviations in order to study general trends.

The methodology creates the western calendar layout, because most countries have adopted this format. The main difference between countries is the use of different languages for labeling, which is supported by the software. Formats beyond the western calendar, or six-weeks and tetris-like layouts could be achieved by slightly tweaking the modular arithmetic approach. These features will be added as new options for the future.

### 2019-04-26 main.tex
added a couple of sentences to future work

When \texttt{polar\ =\ TRUE}, a polar transformation is carried out on the data. The computation is similar to the one described in \citet{Wickham2012glyph}. The resulting plot is star glyphs embedded in the monthly calendar layout. Star glyphs are time series lines transformed in polar coordinates.

@@

\caption{Calendar displays for each household using common scales. We can precisely tell each indidual's vacation days to take off and the overnight use for household 2.}\label{fig:calendar-elec}
\end{figure}

>>>>

When \texttt{polar\ =\ TRUE}, a polar transformation is carried out on the data. The computation is similar to the one described in \citet{Wickham2012glyph}. The resulting plot is star glyphs---time series lines transformed in polar coordinates---embedded in the monthly calendar layout.

@@

\caption{Calendar displays for each household using common scales. We can precisely tell each indidual's vacation days taking off and the overnight use for household 2 in mid January.}\label{fig:calendar-elec}
\end{figure}
